\textbf{ Interpretable Gaussian Processes for Stellar Variability }

### 2021-01-19 tex/ms.tex
finished discussion

The first point is illustrated in the toy example in
Figure~\ref{fig:mean_normalization}. \xxx{As it has been pointed out before \citep{?},
    we will not spend too much time discussing it,} other than to say that the
flux normalization introduces a degeneracy between the total spot coverage
of a star and the contrast of any individual feature on the surface.
\xxx{While this is a formally perfect degeneracy for a single light curve, we can
    again resort to ensemble statistics across many light curves to break it;
    we discuss this further in \S\ref{sec:breaking_baseline_degeneracy}.
    NO WE CAN'T. Talk about this in more detail.}

>>>>

The first point is illustrated in the toy example in
Figure~\ref{fig:mean_normalization}. As it has been pointed out before
\citep[e.g.,][]{Basri2018},
we will not spend too much time discussing it, other than to say that the
flux normalization introduces a degeneracy between the total spot coverage
of a star and the contrast of any individual feature on the surface.
The two stars in the figure have different numbers of spots, different
spot contrasts, and different total spot coverage. In ``absolute'' units, in which
the flux is measured as a fraction of the flux of an unspotted star, the two
light curves are distinct (top panel). However, we can only measure these light
curves up to an unknown multiplicative factor. Normalizing these light curves
to the ``continuum'' level yields the curves in the bottom panel, which are
\emph{perfectly} indistinguishable from each other. Normalization to the mean,
median, or any other statistic of the light curve does not help break this
degeneracy, which is inherent to relative photometry. While one could instead \emph{fit}
for the normalization as a latent variable, there is no information in the data
that can help break it, so the result will be entirely determined by the prior.%
\footnote{%
In principle, the maximum level of a light curve could set a lower limit on
the location of the baseline. However, this applies only if the surface is
known to be made up of \emph{exclusively} dark spots. The presence of bright
spots (faculae), which are common on the Sun, make it effectively impossible
for one to infer the baseline from single-band relative photometry alone.
}
We discuss these issues further in \S\ref{sec:breaking_baseline_degeneracy}.
